Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-05 tex/MesnardoBarba2019.tex
Add a box with Docker terminologies

@@

>>>>

\definecolor{lightgray}{rgb}{0.95,0.95,0.95}

@@

\begin{figure*}
    \begin{center}
        \colorbox{lightgray}{
        \begin{minipage}[c]{14cm}
        \bigskip
        \small \sffamily{
        \subsection*{Docker Terminologies:}
{\sf \footnotesize
\textbf{Docker}--- An open source OS-level virtualization software to create and run multiple independent, isolated, and portable containers on the same host Operating System.\\
\vspace{0.1cm}\\
\textbf{Docker Image}--- Union of layered filesystems stacked on top of each other. Each layer defines a set of differences from the previous layer. A user composes (builds) a Docker image using a \texttt{Dockerfile}, usually starting from a base image (such as \texttt{ubuntu:16.04}).\\
\vspace{0.1cm}\\
\textbf{Docker Container}--- A standardized unit created from a Docker image to deploy an application or a runtime environment. A Docker container can be seen as an instance of a Docker image that includes an additional writable layer at the top of the layered stack. When a container is deleted, so is the writable layer, while the image remains unchanged.\\
\vspace{0.1cm}\\
\textbf{Dockerfile}--- An ASCII file including the sequence of instructions to create a Docker image for the computational runtime environment. A Dockerfile contains Docker keywords such as \texttt{FROM}, \texttt{RUN}, or \texttt{COPY}. Each instructions in the \texttt{Dockerfile} creates a layer in the Docker image.\\
\vspace{0.1cm}\\
\textbf{DockerHub}--- The official registry of Docker Inc.; a cloud-based registry service to store, share, and retrieve (public or private) Docker images.\\
}}
        \vspace{0.2cm}
        \end{minipage}}
    \end{center}
\end{figure*}
